\documentclass[a4paper,9pt]{article}
\usepackage{cv}
\name{Andreas Christian M\"uller}
\info{Email: & \href{mailto:andreas.mueller.ml+cv@gmail.com}{andreas.mueller.ml+cv@gmail.com}\\
      Web: & \url{http://amueller.io}\\}
 
\bibliography{cv}
\addtocategory{selected}{amuellerintropython, scherer2010evaluation, muller2012information, abraham2014machine, muellerpystruct, varoquaux2015scikit}

\begin{document}

\maketitle

\section{Current Position}
\begin{tabular}{lll}
    since 2020 & \textbf{Principle Research SDE at Microsoft}
               & Research and open source activities in the Gray Systems Lab.
\end{tabular}

\section{Past Positions}
\begin{tabular}{lll}
    2010--2013 & \textbf{PhD Student at the Department of Computer Science, University of Bonn, Germany}\\
         & Advisor: Prof.\ Sven Behnke. \\
    2013--2014 & \textbf{Machine Learning Scientist at Amazon Development Center Germany}\\
              & Design and implementation of large-scale machine learning and\\
              & computer vision applications.\\
    2014--2016 & \textbf{Research Engineer at the NYU Center for Data Science}\\
               & Development of open source tools for machine learning and data science.\\
    2016--2020 & \textbf{Lecturer in Discipline, Associate Research Scientist at Columbia University}\\
               & Teaching in the Data Science Master program, \\
               & scikit-learn development and various research activities.
\end{tabular}

\section{Professional Activities}
\subsection{Awarded Grants}
\begin{itemize}
    \item \emph{Scikit-learn maintenance and enhancement to gradient boosting and search} (PI). Chan-Zuckerberg \$150k. 2019-2020.
    \item \emph{Extension \& Maintenance of Scikit-learn} (PI). Alfred P. Sloan Foundation. \$313k. 2017-2019.
    \item \emph{Analysis and Extension of Scikit-learn} (PI). Bloomberg. \$63k. 2017-2018.
    \item \emph{SI2-SSE: Improving Scikit-learn usability and automation} (PI). NSF. \$400k. 2017-2020.
    \item \emph{Building Blocks and Search Improvements for Automated Machine Learning} (PI). DARPA. \$351k. 2018.
\end{itemize}

\subsection{Open Source Contributions}
\begin{itemize}
    \item Core developer and member of the Technical Committee for the machine learning package ``scikit-learn''\footnote{\url{http://scikit-learn.org/}}.
    \item Creator of the ``dabl``\footnote{\url{http://dabl.github.io}} library for human-in-the-loop data science.
    \item Creator of the Python package ``PyStruct''\footnote{\url{http://pystruct.github.org/}} for structured prediction.
    \item Co-author of ``CUV'', a C++ and Python interface for CUDA,
        targeted at deep learning.\footnote{\url{https://github.com/deeplearningais/CUV}}
    \item Contributor to the Python computer vision package ``scikit-image''\footnote{\url{http://scikit-image.org/}}.
\end{itemize}

\subsection{Journal Editorial Board}
\begin{itemize}
    \item Action Editor, Journal of Machine Learning Research, OSS Track
\end{itemize}
\printbib{selected}

\end{document}
